### 2023-11-20 python_excel_ite.tex
edits for revision

\usepackage[most]{tcolorbox}
\usepackage{minted}
\tcbuselibrary{minted} % tcolorbox minted library, required to use the "minted" tcb listing engine (this library is not loaded by the option [most])
\usepackage[colorlinks]{hyperref} % ALWAYS load this package LAST

@@

% In the reviewing and copyediting stage enter the manuscript number.
%\MANUSCRIPTNO{} % When the article is logged in and DOI assigned to it,
                 %   this manuscript number is no longer necessary

@@

% Title or shortened title suitable for running heads. Sample:
% \RUNTITLE{Bundling Information Goods of Decreasing Value}
% Enter the (shortened) title:
\RUNTITLE{Spreadsheet-ish modeling with Python}

% Full title. Sample:
% \TITLE{Bundling Information Goods of Decreasing Value}
% Enter the full title:
\TITLE{Spreadsheet-ish modeling with Python}

@@

\begin{figure*}[!htbp]
	\centering
	\includegraphics[scale=0.5]{images/cells_edit_mode.png}
	\caption{Notebook cells in edit model}
	\label{fig:cells_edit_mode}
\end{figure*}

\begin{figure*}[!htbp]
	\centering
	\includegraphics[scale=0.5]{images/cells_after_running.png}
	\caption{Notebook cells after execution}
	\label{fig:cells_after_running}
\end{figure*}

@@

\begin{figure}[!htbp]
	\includegraphics[width=1.0\textwidth]{images/output_2_0.png}
	\caption{Typical spreadsheet model}
	\label{fig:xl_model}
\end{figure}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[scale=0.5]{images/model_inputs.png}
	\caption{Instantiating model inputs and creating output formulas}
	\label{fig:model_inputs}
\end{figure}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[scale=0.5]{images/function_datatable.png}
	\caption{A 2-way data table}
	\label{fig:function_datatable}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[scale=0.5]{images/datatable_scatter.png}
	\caption{Scatter plot based on 2-way data table}
	\label{fig:datatable_scatter}
\end{figure}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1.0\textwidth]{images/two_way_dt.png}
	\caption{Faceted plot based on 2-way data table}
	\label{fig:2way_dt}
\end{figure}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[scale=0.5]{images/oo_sim_design_specs.png}
	\caption{Design specification for \code{simulate()} function}
	\label{fig:oo_sim_design_specs}
\end{figure}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1.0\textwidth]{images/boxplots.png}
	\caption{Profit boxplots by order quantity}
	\label{fig:boxplot}
\end{figure}

@@

\begin{figure}[!htbp]
	\centering
	\includegraphics[scale=0.5]{images/sim_wrapup.png}
	\caption{Closing thoughts in simulation notebook}
	\label{fig:sim_wrapup}
\end{figure}

@@

% CASE 1: BiBTeX used to constantly update the references 
%   (while the paper is being written).
\bibliographystyle{informs2014} % outcomment this and next line in Case 1
\bibliography{python_excel.bib} % if more than one, comma separated

% CASE 2: BiBTeX used to generate mypaper.bbl (to be further fine tuned)
%\input{mypaper.bbl} % outcomment this line in Case 2

>>>>

\usepackage[most]{tcolorbox}
\usepackage{graphicx}
%\usepackage{minted}
%\tcbuselibrary{minted} % tcolorbox minted library, required to use the "minted" tcb listing engine (this library is not loaded by the option [most])
\usepackage[colorlinks]{hyperref} % ALWAYS load this package LAST

@@

% In the reviewing and copyediting stage enter the manuscript number.
\MANUSCRIPTNO{} % When the article is logged in and DOI assigned to it,
                 %   this manuscript number is no longer necessary

@@

% Title or shortened title suitable for running heads. Sample:
% \RUNTITLE{Bundling Information Goods of Decreasing Value}
% Enter the (shortened) title:
\RUNTITLE{Spreadsheet modeling and wrangling with Python}

% Full title. Sample:
% \TITLE{Bundling Information Goods of Decreasing Value}
% Enter the full title:
\TITLE{Spreadsheet modeling and wrangling with Python}

@@

\begin{figure*}[!htbp]
\centering
\includegraphics[scale=0.5]{cells_edit_mode}
\caption{Notebook cells in edit model}
\label{fig:cells_edit_mode}
\end{figure*}

\begin{figure*}[!htbp]
\centering
\includegraphics[scale=0.5]{cells_after_running}
\caption{Notebook cells after execution}
\label{fig:cells_after_running}
\end{figure*}

@@

\begin{figure}[!htbp]
\includegraphics[width=1.0\textwidth]{output_2_0}
\caption{Typical spreadsheet model}
\label{fig:xl_model}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[scale=0.5]{model_inputs}
\caption{Instantiating model inputs and creating output formulas}
\label{fig:model_inputs}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[scale=0.5]{function_datatable}
\caption{A 2-way data table}
\label{fig:function_datatable}
\end{figure}

\begin{figure}[!htbp]
\centering
\includegraphics[scale=0.5]{datatable_scatter}
\caption{Scatter plot based on 2-way data table}
\label{fig:datatable_scatter}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=1.0\textwidth]{two_way_dt}
\caption{Faceted plot based on 2-way data table}
\label{fig:2way_dt}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[scale=0.5]{oo_sim_design_specs}
\caption{Design specification for \code{simulate()} function}
\label{fig:oo_sim_design_specs}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=1.0\textwidth]{boxplots}
\caption{Profit boxplots by order quantity}
\label{fig:boxplot}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[scale=0.5]{sim_wrapup}
\caption{Closing thoughts in simulation notebook}
\label{fig:sim_wrapup}
\end{figure}

@@

% CASE 1: BiBTeX used to constantly update the references 
%   (while the paper is being written).
%\bibliographystyle{informs2014} % outcomment this and next line in Case 1
%\bibliography{python_excel.bib} % if more than one, comma separated

% CASE 2: BiBTeX used to generate mypaper.bbl (to be further fine tuned)
%\input{mypaper.bbl} % outcomment this line in Case 2
\begin{thebibliography}{29}
	\providecommand{\natexlab}[1]{#1}
	\providecommand{\url}[1]{\texttt{#1}}
	\providecommand{\urlprefix}{URL }

	\bibitem[{Albright \protect\BIBand{}
		Winston(2016)}]{albrightBusinessAnalyticsData2016}
	Albright SC, Winston WL (2016) \emph{Business {{Analytics}}: {{Data Analysis}}
		\& {{Decision Making}} - {{Standalone}} Book} ({Boston, MA}: {Cengage
		Learning}), 6th edition edition, ISBN 978-1-305-94754-2.

	\bibitem[{{Audrey Roy and Cookiecutter
			community}(2012)}]{audreyroyandcookiecuttercommunityCookiecutterBetterProject2012}
	{Audrey Roy and Cookiecutter community} (2012) \emph{Cookiecutter: {{Better}}
		Project Templates}.

	\bibitem[{Barba et~al.(2019)Barba, Barker, Blank, Brown, Downey, George, Heagy,
		Mandli, Moore, Lippert et~al.}]{barba2019teaching}
	Barba LA, Barker LJ, Blank DS, Brown J, Downey AB, George T, Heagy LJ, Mandli
	KT, Moore JK, Lippert D, et~al. (2019) Teaching and learning with
	{{Jupyter}}. \emph{Recuperado: https://jupyter4edu. github.
		io/jupyter-edu-book} .

	\bibitem[{Buezen \protect\BIBand{}
		Timbers(2022)}]{buezenWelcomePythonPackages2022}
	Buezen T, Timbers T (2022) Welcome to {{Python Packages}}! \textemdash{}
	{{Python Packages}}. https://py-pkgs.org/.

	\bibitem[{Camm et~al.(2020)Camm, Cochran, Fry, \protect\BIBand{}
		Ohlmann}]{camm2020business}
	Camm JD, Cochran JJ, Fry MJ, Ohlmann JW (2020) \emph{Business Analytics}
	({Cengage Learning}).

	\bibitem[{Canny(2013)}]{cannyPythonpptx2013}
	Canny S (2013) Python-pptx. https://python-pptx.readthedocs.io/en/latest/.

	\bibitem[{Cimpanu(2017)}]{cimpanuMicrosoftConsidersAdding2017}
	Cimpanu C (2017) Microsoft {{Considers Adding Python}} as an {{Official
			Scripting Language}} to {{Excel}}.
	https://www.bleepingcomputer.com/news/microsoft/microsoft-considers-adding-python-as-an-official-scripting-language-to-excel/.

	\bibitem[{Grus(2018)}]{grusDonNotebooks2018}
	Grus J (2018) I don't like notebooks ({JupyterCon 2018 (New York)}).

	\bibitem[{Harris et~al.(2020)Harris, Millman, {van der Walt}, Gommers,
		Virtanen, Cournapeau, Wieser, Taylor, Berg, Smith, Kern, Picus, Hoyer, {van
			Kerkwijk}, Brett, Haldane, {del R{\'i}o}, Wiebe, Peterson,
		{G{\'e}rard-Marchant}, Sheppard, Reddy, Weckesser, Abbasi, Gohlke,
		\protect\BIBand{} Oliphant}]{harris2020array}
	Harris CR, Millman KJ, {van der Walt} SJ, Gommers R, Virtanen P, Cournapeau D,
	Wieser E, Taylor J, Berg S, Smith NJ, Kern R, Picus M, Hoyer S, {van
		Kerkwijk} MH, Brett M, Haldane A, {del R{\'i}o} JF, Wiebe M, Peterson P,
	{G{\'e}rard-Marchant} P, Sheppard K, Reddy T, Weckesser W, Abbasi H, Gohlke
	C, Oliphant TE (2020) Array programming with {{NumPy}}. \emph{Nature}
	585(7825):357--362,
	\urlprefix\url{http://dx.doi.org/10.1038/s41586-020-2649-2}.

	\bibitem[{Johnson(2020)}]{johnson2020benefits}
	Johnson JW (2020) Benefits and pitfalls of jupyter notebooks in the classroom.
	\emph{Proceedings of the 21st Annual Conference on Information Technology
		Education}, 32--37.

	\bibitem[{{Jupyter Team}(2015)}]{jupyterteamProjectJupyterDocumentation2015}
	{Jupyter Team} (2015) Project jupyter documentation.
	https://docs.jupyter.org/en/latest/.

	\bibitem[{McKinney(2022)}]{mckinney2022python}
	McKinney W (2022) \emph{Python for Data Analysis} ({O'Reilly}).

	\bibitem[{Moffitt(2022)}]{moffittPracticalBusinessPython2022}
	Moffitt C (2022) Practical {{Business Python}}. https://pbpython.com/.

	\bibitem[{Nelson(2024)}]{nelsonSoftwareEngineeringData2024}
	Nelson C (2024) \emph{Software {{Engineering}} for {{Data Scientists}}}
	({O'Reilly}), ISBN 978-1-09-813619-2.

	\bibitem[{Pedregosa et~al.(2011)Pedregosa, Varoquaux, Gramfort, Michel,
		Thirion, Grisel, Blondel, Prettenhofer, Weiss, Dubourg, Vanderplas, Passos,
		Cournapeau, Brucher, Perrot, \protect\BIBand{} Duchesnay}]{scikit-learn}
	Pedregosa F, Varoquaux G, Gramfort A, Michel V, Thirion B, Grisel O, Blondel M,
	Prettenhofer P, Weiss R, Dubourg V, Vanderplas J, Passos A, Cournapeau D,
	Brucher M, Perrot M, Duchesnay E (2011) Scikit-learn: {{Machine}} learning in
	{{Python}}. \emph{Journal of Machine Learning Research} 12:2825--2830.

	\bibitem[{Perez \protect\BIBand{} Granger(2015)}]{perez2015project}
	Perez F, Granger BE (2015) Project {{Jupyter}}: {{Computational}} narratives as
	the engine of collaborative data science. \emph{Retrieved September}
	11(207):108.

	\bibitem[{Perkel(2018)}]{perkel2018jupyter}
	Perkel JM (2018) Why {{Jupyter}} is data scientists' computational notebook of
	choice. \emph{Nature} 563(7732):145--147.

	\bibitem[{Powell(2001)}]{powellTeachingModelingManagement2001}
	Powell SG (2001) Teaching {{Modeling}} in {{Management Science}}. \emph{INFORMS
		Transactions on Education} 1(2):62--67, ISSN 1532-0545,
	\urlprefix\url{http://dx.doi.org/10.1287/ited.1.2.62}.

	\bibitem[{Powell \protect\BIBand{}
		Baker(2019)}]{powellBusinessAnalyticsArt2019}
	Powell SG, Baker KR (2019) \emph{Business {{Analytics}}: {{The Art}} of
		{{Modeling With Spreadsheets}}, 5th {{Edition}} | {{Wiley}}}.

	\bibitem[{Ragsdale(2017)}]{ragsdaleSpreadsheetModelingDecision2017}
	Ragsdale C (2017) \emph{Spreadsheet {{Modeling}} \& {{Decision Analysis}}: {{A
				Practical Introduction}} to {{Business Analytics}}} ({Australia}: {Cengage
		Learning}), 8th edition edition, ISBN 978-1-305-94741-2.

	\bibitem[{Rodrigues(2023)}]{rodriguesBuildingReproducibleAnalytical2023}
	Rodrigues B (2023) Building reproducible analytical pipelines with {{R}}.
	https://raps-with-r.dev/.

	\bibitem[{Rule et~al.(2018)Rule, Birmingham, Zuniga, Altintas, Huang, Knight,
		Moshiri, Nguyen, Rosenthal, P{\'e}rez et~al.}]{rule2018ten}
	Rule A, Birmingham A, Zuniga C, Altintas I, Huang SC, Knight R, Moshiri N,
	Nguyen MH, Rosenthal SB, P{\'e}rez F, et~al. (2018) Ten simple rules for
	reproducible research in {{Jupyter}} notebooks. \emph{arXiv preprint
		arXiv:1810.08055} .

	\bibitem[{Savage(2012)}]{savageFlawAveragesWhy2012}
	Savage SL (2012) \emph{The {{Flaw}} of {{Averages}}: {{Why We Underestimate
				Risk}} in the {{Face}} of {{Uncertainty}}} ({Hoboken, New Jersey}: {Wiley}),
	1st edition edition, ISBN 978-1-118-07375-9.

	\bibitem[{Treadway(2023)}]{treadwaySoftwareEngineeringData2023}
	Treadway A (2023) \emph{Software {{Engineering}} for {{Data Scientists}}}
	({Manning}).

	\bibitem[{Ufford et~al.(2019)Ufford, {Pacer, M}, {Seal, Matthew},
		\protect\BIBand{} {Kelley, Kyle}}]{uffordInteractiveNotebookInnovation2019}
	Ufford M, {Pacer, M}, {Seal, Matthew}, {Kelley, Kyle} (2019) Beyond
	{{Interactive}}: {{Notebook Innovation}} at {{Netflix}}.
	https://netflixtechblog.com/notebook-innovation-591ee3221233.

	\bibitem[{Virtanen et~al.(2020)Virtanen, Gommers, Oliphant, Haberland, Reddy,
		Cournapeau, Burovski, Peterson, Weckesser, Bright, {van der Walt}, Brett,
		Wilson, Millman, Mayorov, Nelson, Jones, Kern, Larson, Carey, Polat, Feng,
		Moore, VanderPlas, Laxalde, Perktold, Cimrman, Henriksen, Quintero, Harris,
		Archibald, Ribeiro, Pedregosa, {van Mulbregt}, \protect\BIBand{} {SciPy 1.0
			Contributors}}]{2020SciPy-NMeth}
	Virtanen P, Gommers R, Oliphant TE, Haberland M, Reddy T, Cournapeau D,
	Burovski E, Peterson P, Weckesser W, Bright J, {van der Walt} SJ, Brett M,
	Wilson J, Millman KJ, Mayorov N, Nelson ARJ, Jones E, Kern R, Larson E, Carey
	CJ, Polat {\.I}, Feng Y, Moore EW, VanderPlas J, Laxalde D, Perktold J,
	Cimrman R, Henriksen I, Quintero EA, Harris CR, Archibald AM, Ribeiro AH,
	Pedregosa F, {van Mulbregt} P, {SciPy 10 Contributors} (2020) {{SciPy}} 1.0:
	{{Fundamental}} algorithms for scientific computing in python. \emph{Nature
		Methods} 17:261--272,
	\urlprefix\url{http://dx.doi.org/10.1038/s41592-019-0686-2}.

	\bibitem[{Walls(2023)}]{wallsMathematicalPython2023}
	Walls P (2023) Mathematical {{Python}}.
	https://github.com/patrickwalls/mathematicalpython.

	\bibitem[{Wickham(2014)}]{wickhamTidyData2014}
	Wickham H (2014) Tidy {{Data}}. \emph{Journal of Statistical Software}
	59:1--23, ISSN 1548-7660,
	\urlprefix\url{http://dx.doi.org/10.18637/jss.v059.i10}.

	\bibitem[{Winston \protect\BIBand{}
		Albright(2018)}]{winstonPracticalManagementScience2018}
	Winston WL, Albright SC (2018) \emph{Practical {{Management Science}}}
	({Australia ; Boston, MA}: {Cengage Learning}), 6th edition edition, ISBN
	978-1-337-40665-9.

\end{thebibliography}
